---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(CodeClanData)
```

Q1
```{r}
drinks_content
```

```{r}
ncol(drinks_content)
```
```{r}
ncol(drinks_content)
```
```{r}
names(drinks_content)
```
```{r}
summary((drinks_content))
```

Q2  

```{r}
drinks_content %>% filter(!is.na(Calories))  %>%   select(Beverage,Beverage_category,Beverage_prep, Calories)


```
Q3

```{r}

mutate(drinks_content, calorie_diff = (Calories - 135) )
```
Q4

```{r}
mean_calories <- drinks_content %>% group_by(Beverage_category) %>% arrange(Calories) %>% select(Calories, Beverage_category, Beverage,Beverage_prep)
mean_calories
```

```{r}
head(mean_calories,3)
```



```{r}
mean_calories <- drinks_content %>% group_by(Beverage_category) %>% arrange(desc(Calories))    %>% select(Calories, Beverage_prep, Beverage,Beverage_category)
mean_calories
```




The group_by is not doing what I want as I expected it to roll up the data by beverage_category. I was thinking we should see only one category and its total.

Three categories with the most calories are : 	Signature Espresso Drinks, Frappuccino® Blended Coffee, Frappuccino® Blended Coffee.

The minimum calorie drinks are: Tazo Tea Drinks (short, tall, grande)

Q5

Had problems with the rollup of data as above so wasn't getting the mean per catgory and tried it by hand,



```{r}
mean_calories <- drinks_content %>% group_by(Beverage_prep) %>% filter(Beverage_prep == "Grande") %>% select(Calories, Beverage_prep, Beverage,Beverage_category) 
mean_calories


```
```{r}
mean_calories <- drinks_content %>% group_by(Beverage_prep) %>% filter(Beverage_prep == "Tall") %>% select(Calories, Beverage_prep, Beverage,Beverage_category)  
mean_calories
```


```{r}
mean_calories <- drinks_content %>% group_by(Beverage_prep) %>% filter(Beverage_prep == "2% Milk") %>% select(Calories, Beverage_prep, Beverage,Beverage_category)  
mean_calories
```

etc. etc.etc.

Q6

```{r}
mutate(drinks_content, avg_cal = mean(Calories))  %>% head(1) %>% select(avg_cal)

```

510	2% Milk	White Chocolate Mocha (Without Whipped Cream)


```{r}

drinks_content  %>% select(Calories) %>% max()
```


Q7.

	Brewed Coffee	Short = 3 cals (as above)
```{r}
	drinks_content  %>% filter(Beverage_category == "Coffee" ) %>% filter( Calories == min(Calories)  )
```
	

	